Matching Bullets

### 2015-12-08 imaging-paper.Rnw
slowly getting rid of all the little things

options(replace.assign=TRUE,scipen=3)
@

@@

\hh{XXX add parameter estimates? $\hat{r} \approx 4500$ - indicating a 9 mm bullet, amount of degrees covered by land?  }
The scatterplot in Figure~\ref{fig:residual} shows the residuals of such a fit. The residuals are dominated, as expected, by the grooves, which show up as large positive residuals. For a surface cross cut at $x = 100$ there is a residual circular structure that does not show up for all cross sections.

@@

\section{Application}
We have implemented a web interface to automate many of the steps outlined in the previous section. The web interface, developed using Shiny \cite{shiny}, allows a user to upload two x3p files representing scans of a bullet between two grooves. A 3D viewer, using Plotly \cite{plotly}, allows the user to rotate and zoom to examine surface features of the images. A screenshot of the application is available in Figure \ref{fig:app}. The application is available at the url \url{http://erichare.shinyapps.io/x3prproto}.

\begin{figure*}
\includegraphics[width=\textwidth]{images/app.png}
\caption{\label{fig:app}{Screenshot of the web interface for analyzing bullet images.}}
\end{figure*}

@@

ggplot() + 
  geom_rect(aes(xmin = xmin, xmax = xmax, fill=factor(type)), ymin = -6, ymax=6.5,  data = lines, alpha=0.2, show.legend = FALSE) +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
  ylim(c(-6,6.5)) + theme_bw() +
  geom_line(data=lofX, aes(x=y, y=l30, group=bullet, colour=bullet)) +
  scale_colour_brewer("", palette="Set1") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey60", 0.5)) +
    theme(legend.position = c(1,1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab(expression(paste("Crosscut values (in ",mu,"m)", sep=""))) +
  xlab("y")
@
    }
\end{subfigure}
\caption{\label{fig:match}Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between crosscuts (c).}
\end{figure}

@@

\hh{The automated matching routine is then as follows:
Identify a stable region for each bullet and pick the lowest crosscut level in this region (assumption here: lower crosscut levels show better expression of individual marks XXX need to still check)

@@

\hh{XXX needs more work: how does crosscut impact the results?  For the same bullet: how far apart can crosscuts be to still result in a match?}

@@

\hh{Things we discussed}
\begin{enumerate}
\item the Hamby study only includes 35 bullets - this is not a particularly realistic scenario for automatic matching. Adding more non-matches into the mix is going to make things more realistic. 
\item parameter optimization is going to drive some of the matches
\item involve multiple crosscuts for each bullet in a match?
\end{enumerate}

>>>>

options(replace.assign=TRUE,scipen=3, digits=2)
@

@@

%\hh{XXX add parameter estimates? $\hat{r} \approx 4500$ - indicating a 9 mm bullet, amount of degrees covered by land?  }
The scatterplot in Figure~\ref{fig:residual} shows the residuals of such a fit.
\hh{In this instance, the radius is estimated as $\hat{r} = \Sexpr{pars$radius}\mu m = \Sexpr{pars$radius/1000}mm$, which is consistent with a 9 mm bullet fired in a Ruger P-85. }
The residuals are dominated, as expected, by the grooves, which show up as large positive residuals. For a surface cross cut at $x = 100$ there is a residual circular structure that does not show up for all cross sections.

@@

\section{Application}
We have implemented a web interface to automate many of the steps outlined in the previous section. The web interface, developed using Shiny \cite{shiny}, allows a user to upload two x3p files representing scans of a bullet between two grooves. A 3D viewer, using Plotly \cite{plotly}, allows the user to rotate and zoom to examine surface features of the images. A screenshot of the application is shown in Figure~\ref{fig:app}. The application is available at the url \url{http://erichare.shinyapps.io/x3prproto}.

\begin{figure*}
\includegraphics[width=\textwidth]{images/app.png}
\caption{\label{fig:app}{Screenshot of the web interface for analyzing bullet images. \hh{The shot shows two lands from the Hamby study. Although the lands are a match, this is visually very hard to confirm.}}}
\end{figure*}

@@

ggplot() + 
  geom_rect(aes(xmin = xmin, xmax = xmax, fill=factor(type)), ymin = -6, ymax=6.5,  data = lines, alpha=0.2, show.legend = FALSE) +
  theme(legend.position="bottom") +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
  ylim(c(-6,6.5)) + theme_bw() +
  geom_line(data=lofX, aes(x=y, y=l30, group=bullet, colour=bullet)) +
  scale_colour_brewer("", palette="Set1") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey60", 0.5)) +
    theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
  ylab(expression(paste("Crosscut values (in ",mu,"m)", sep=""))) +
  xlab("y")
@
    }
\end{subfigure}
\caption{\label{fig:match}Matching striation marks: smooth (a), identify peaks and valley (b), and match peaks and valleys between crosscuts (c).}
\end{figure}

@@

\subsection{Automatic Matching Algorithm}
\hh{The automated matching routine is then as follows:
Identify a stable region for each bullet and pick the lowest crosscut level in this region (assumption here: lower crosscut levels show better expression of individual marks XXX need to still check)

@@

@@

\hh{Things we discussed}
\begin{enumerate}
\item the Hamby study only includes 35 bullets - this is not a particularly realistic scenario for automatic matching. Adding more non-matches into the mix is going to make things more realistic. 
\item parameter optimization is going to drive some of the matches
\item involve multiple crosscuts for each bullet in a match?
\item assessing different crosscuts at the same bullet allows us to assess a land's quality in terms of how stable it is -- generally, break-off patterns are less stable. }

\end{enumerate}
